Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-18 tex/sections/consensus.tex
Update subsection "Initiating the Recovery Protocol"
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

A validator enters the agreement protocol if he
receives a request that is signed by more than half of the total stake
of the validators and its start time has not passed. The validator calculates
the stake values based on the staking database of the last final block in his blockchain without
considering the \texttt{online}/\texttt{offline} status of validators.

@@

A honest user during a session only final-votes a single proposal. This ensures that as long as $2/3$ of the total
stake of the system is controlled by honest users, two different proposal can not get $2/3$ final-votes. However, when
a user sees $2/3$ final-votes for a proposal, he can not be sure that other users have also seen those votes and have
ended the voting phase. If enough stake is still in the voting phase the agreement protocol may confirm a
different proposal.

@@

When a validator does not receive any blocks for \texttt{blockTimeOut} amount of time, or when he sees an
evidence which proves the delegates are malicious, he initiates the recovery protocol.

To do so, first the validator activates the censorship resilient mode of his networking module, then he checks the
validity of the blocks that do not have a validators' certificate and determines the
last valid block of his blockchain.

In the next step, he will sign and broadcast an \textbf{emergency fork request} message, alongside some useful metadata
such as the last valid block of his blockchain and the evidence of delegates' misbehaviour.\footnote{this metadata is
not a part of the fork request.}

If the reserve committee of delegates is already active, or if a validator sees a valid fork request signed
by more than half of the total online stake of the validators, but does not receive the fork
block after a certain amount of time, he will sign and broadcast a request for
\textbf{emergency agreement} on a new reserve committee. The agreement on new delegates usually needs user
interaction and is not a fully automatic process.

The evidence which proves a committee of delegates is malicious is an invalid block that is signed by at least
one delegate:
\begin{itemize}
    \item a block that is not conditionally valid
    \item two different blocks with the same parent
    \item a block that has an invalid format
\end{itemize}

@@

In a proof of stake system the influence of a user in the consensus protocol should be proportional to the amount
of stake the user has in the system. Conventionally in these systems, a user's stake is considered to be equal with the
amount of native system tokens, he has "staked" in the system. A user stakes his tokens by locking them in
his account or a separate staking account for some period of time. During this time, he will not be able to transfer
his tokens.

>>>>

A validator enters the agreement protocol if he
receives a request that is signed by more than half of the total stake
of the validators and its start time has not passed. The validator calculates
the stake values based on the staking database of the last \textbf{final} block in his blockchain without
considering the \texttt{online}/\texttt{offline} status of validators.

@@

A honest user during a session only final-votes a single proposal. This ensures that as long as $2/3$ of the total
stake of the system is controlled by honest users, two different proposals can not get $2/3$ final-votes. However, when
a user sees $2/3$ final-votes for a proposal, he can not be sure that other users have also seen those votes and have
ended the voting phase. If enough stake is still in the voting phase the agreement protocol may confirm a
different proposal.

@@

When the validator software does not receive any blocks for \texttt{blockTimeOut} amount of time, or when it observes an
evidence which proves the delegates are malicious, after prompting the user and after his confirmation, it will
initiate the recovery protocol.

To do so, first the validator software activates the censorship resilient mode of the networking module, then it checks
the validity of the blocks that do not have a validators certificate and determines the last valid block of its
version of the blockchain.

In the next step, it will sign and broadcast an \textbf{emergency fork request} message, alongside some useful metadata
such as the last valid block of its blockchain and the evidence of delegates' misbehaviour.\footnote{this metadata is
not a part of the fork request.} Before starting the recovery protocol, validators try to synchronize their blockchains
as much as possible.

If the reserve committee of delegates is already active, or if the validator software sees a valid fork request signed
by more than half of the total online stake of the validators, but does not receive the fork
block after a certain amount of time, after user confirmation, it will sign and broadcast a request for
\textbf{emergency agreement} on a new reserve committee. The agreement on new delegates usually needs user
interaction and is not a fully automatic process.

The evidence which proves a committee of delegates is malicious is an invalid block that is signed by at least
one delegate:
\begin{itemize}
    \item a block that is not conditionally valid
    \item two different blocks with the same parent
\end{itemize}

@@

In a proof of stake system the influence of a user in the consensus protocol should be proportional to the amount
of stake the user has in the system. Conventionally in these systems, a user's stake is considered to be equal with the
amount of native system tokens, he has ``staked'' in the system. A user stakes his tokens by locking them in
his account or a separate staking account for some period of time. During this time, he will not be able to transfer
his tokens.
